From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-09 Pi+/paper/equivalence.tex
General formatting
Update

\begin{toappendix}
  \todo{What is U?}
  \begin{proposition}
    We can form a weak 2-category $\PiCat$ with
    \begin{itemize}
      \item $\PiLang$ types for 0-cells,
      \item for $X, Y : U$, a collection of 1-cells $X \iso Y$,
      \item for $p, q : X \iso Y$, a collection of 2-cells $p \Iso q$.
    \end{itemize}
  \end{proposition}

  \begin{proposition}
    We can form a weak 2-category $\PiPlusCat$ with
    \begin{itemize}
      \item $\PiPlusLang$ types for 0-cells,
      \item for $X, Y : \UPlus$, a collection of 1-cells $X \isop Y$,
      \item for $p, q : X \isop Y$, a collection of 2-cells $p \Isop q$.
    \end{itemize}
  \end{proposition}

  \begin{proposition}
    We can form a weak 2-category $\PiHatCat$ with
    \begin{itemize}
      \item $\PiHatCat$ types for 0-cells,
      \item for $X, Y : \UHat$, a collection of 1-cells $X \isoh Y$,
      \item for $p, q : X \isoh Y$, a collection of 2-cells $p \Isoh q$.
    \end{itemize}
  \end{proposition}
\end{toappendix}

@@

\begin{proposition}
  There are two symmetric monoidal structures on $\PiPlusCat$, given by $(\zerot, +)$ and $(\onet, \times)$, with
  $\times$ distributing over $+$, giving it a rig structure.
\end{proposition}

@@

\begin{definition}
  \begin{align*}
    \evalt_{0} & : U \to \UPlus                                             \\
    \evalt_{1} & : (c : X \iso Y) \to \evalt_{0}(X) \iso \evalt_{0}(Y)      \\
    \evalt_{2} & : (\alpha : p \Iso q) \to \evalt_{1}(p) \Iso \evalt_{1}(q)
  \end{align*}
\end{definition}

\begin{proposition}
  $\evalt$ gives a rig equivalence between $\PiCat$ and $\PiPlusCat$.
\end{proposition}

@@

\begin{proposition}
  $\PiHatCat$ has a symmetric monoidal structure, with the unit given by 0 and the tensor product given by natural
  number addition.
\end{proposition}

@@

\begin{definition}
  \begin{align*}
    \evalp_{0} & : \UPlus \to \UHat                                                          \\
    \evalp_{1} & : (c : t_{1} \iso t_{2}) \to \evalp_{0}(t_{1}) \isoh \evalp_{0}(t_{2})      \\
    \evalp_{2} & : (\alpha : c_{1} \Iso c_{2}) \to \evalp_{1}(c_{1}) \Isoh \evalp_{1}(c_{2})
  \end{align*}
\end{definition}

@@

\begin{definition}
  \begin{align*}
    \quotep_{0} & : \UHat \to \UPlus                                                            \\
    \quotep_{1} & : (p : X_{1} \isoh X_{2}) \to \quotep_{0}(X_{1}) \iso \quotep_{0}(X_{2})      \\
    \quotep_{2} & : (\alpha : p_{1} \Isoh p_{2}) \to \quotep_{1}(p_{1}) \Iso \quotep_{1}(p_{2})
  \end{align*}
\end{definition}

\begin{proposition}
  $\evalp/\quotep$ give a symmetric monoidal equivalence between $\PiPlusCat$ and $\PiHatCat$.
\end{proposition}

@@

\begin{definition}
  \begin{align*}
    \evalh_{0} & : \UHat \to \UFin                                                          \\
    \evalh_{1} & : (c : t_{1} \isoh t_{2}) \to \evalh_{0}(t_{1}) \id \evalh_{0}(t_{2})      \\
    \evalh_{2} & : (\alpha : c_{1} \Isoh c_{2}) \to \evalh_{1}(c_{1}) \id \evalh_{1}(c_{2})
  \end{align*}
\end{definition}

@@

\begin{definition}
  \begin{align*}
    \quoteh_{0} & : \UFin \to \UHat                                                            \\
    \quoteh_{1} & : (p : X_{1} \id X_{2}) \to \quoteh_{0}(X_{1}) \isoh \quoteh_{0}(X_{2})      \\
    \quoteh_{2} & : (\alpha : p_{1} \id p_{2}) \to \quoteh_{1}(p_{1}) \Isoh \quotet_{1}(p_{2})
  \end{align*}
\end{definition}

@@

\begin{proposition}
  $\evalh/\quoteh$ give a symmetric monoidal equivalence between $\PiHatCat$ and $\UFin$.
\end{proposition}

@@

\begin{definition}[${\gdenot{\blank}} : U \to {\UFin}$]
  \begin{gather*}
    \begin{aligned}
      \gdenot{\blank}_{0} &\defeq \evalh_{0} \comp \evalp_{0} \comp \evalt_{0}
    \end{aligned}
    \qquad
    \begin{aligned}
      \gdenot{\blank}_{1} &\defeq \evalh_{1} \comp \evalp_{1} \comp \evalt_{1}
    \end{aligned}
  \end{gather*}
\end{definition}

\begin{proposition}
  If $c_1, c_2 : X \iso Y$, then $\denot{c_1} = \denot{c_2}$ iff $\gdenot{c_1}_{1} = \gdenot{c_2}_{1}$.
\end{proposition}

>>>>

\begin{toappendix}
  \begin{proposition}
    We can form a weak 2-category $\PiCat$ with
    \begin{itemize}
      \item $\PiLang$ types ($U$) for 0-cells,
      \item for $X, Y : U$, a collection of 1-cells $X \iso Y$,
      \item for $p, q : X \iso Y$, a collection of 2-cells $p \Iso q$.
    \end{itemize}
  \end{proposition}

  \begin{proposition}
    We can form a weak 2-category $\PiPlusCat$ with
    \begin{itemize}
      \item $\PiPlusLang$ types ($\UPlus$) for 0-cells,
      \item for $X, Y : \UPlus$, a collection of 1-cells $X \isop Y$,
      \item for $p, q : X \isop Y$, a collection of 2-cells $p \Isop q$.
    \end{itemize}
  \end{proposition}

  \begin{proposition}
    We can form a weak 2-category $\PiHatCat$ with
    \begin{itemize}
      \item $\PiHatCat$ types ($\UHat$) for 0-cells,
      \item for $X, Y : \UHat$, a collection of 1-cells $X \isoh Y$,
      \item for $p, q : X \isoh Y$, a collection of 2-cells $p \Isoh q$.
    \end{itemize}
  \end{proposition}
\end{toappendix}

@@

\begin{lemma}
  There are two symmetric monoidal structures on $\PiPlusCat$, given by $(\zerot, +)$ and $(\onet, \times)$, with
  $\times$ distributing over $+$, giving it a rig structure.
\end{lemma}

@@

\begin{definition}[$\evalt$]
  \begin{align*}
    \evalt_{0} & : U \to \UPlus                                             \\
    \evalt_{1} & : (c : X \iso Y) \to \evalt_{0}(X) \iso \evalt_{0}(Y)      \\
    \evalt_{2} & : (\alpha : p \Iso q) \to \evalt_{1}(p) \Iso \evalt_{1}(q)
  \end{align*}
\end{definition}

\begin{theorem}
  $\evalt$ gives a rig equivalence between $\PiCat$ and $\PiPlusCat$.
\end{theorem}

@@

\begin{lemma}
  $\PiHatCat$ has a symmetric monoidal structure, with the unit given by 0 and the tensor product given by natural
  number addition.
\end{lemma}

@@

\begin{definition}[$\evalp$]
  \begin{align*}
    \evalp_{0} & : \UPlus \to \UHat                                                          \\
    \evalp_{1} & : (c : t_{1} \isop t_{2}) \to \evalp_{0}(t_{1}) \isoh \evalp_{0}(t_{2})      \\
    \evalp_{2} & : (\alpha : c_{1} \Isop c_{2}) \to \evalp_{1}(c_{1}) \Isoh \evalp_{1}(c_{2})
  \end{align*}
\end{definition}

@@

\begin{definition}[$\quotep$]
  \begin{align*}
    \quotep_{0} & : \UHat \to \UPlus                                                            \\
    \quotep_{1} & : (p : X_{1} \isoh X_{2}) \to \quotep_{0}(X_{1}) \iso \quotep_{0}(X_{2})      \\
    \quotep_{2} & : (\alpha : p_{1} \Isoh p_{2}) \to \quotep_{1}(p_{1}) \Iso \quotep_{1}(p_{2})
  \end{align*}
\end{definition}

\begin{theorem}
  $\evalp/\quotep$ give a symmetric monoidal equivalence between $\PiPlusCat$ and $\PiHatCat$.
\end{theorem}

@@

\begin{definition}[$\evalh$]
  \begin{align*}
    \evalh_{0} & : \UHat \to \UFin                                                          \\
    \evalh_{1} & : (c : t_{1} \isoh t_{2}) \to \evalh_{0}(t_{1}) \id \evalh_{0}(t_{2})      \\
    \evalh_{2} & : (\alpha : c_{1} \Isoh c_{2}) \to \evalh_{1}(c_{1}) \id \evalh_{1}(c_{2})
  \end{align*}
\end{definition}

@@

\begin{definition}[$\quoteh$]
  \begin{align*}
    \quoteh_{0} & : \UFin \to \UHat                                                            \\
    \quoteh_{1} & : (p : X_{1} \id X_{2}) \to \quoteh_{0}(X_{1}) \isoh \quoteh_{0}(X_{2})      \\
    \quoteh_{2} & : (\alpha : p_{1} \id p_{2}) \to \quoteh_{1}(p_{1}) \Isoh \quotet_{1}(p_{2})
  \end{align*}
\end{definition}

@@

\begin{theorem}
  $\evalh/\quoteh$ give a symmetric monoidal equivalence between $\PiHatCat$ and $\UFin$.
\end{theorem}

@@

\begin{definition}
  \begin{gather*}
    \begin{aligned}
      \gdenot{\blank}_{0} &\defeq \evalh_{0} \comp \evalp_{0} \comp \evalt_{0}
    \end{aligned}
    \qquad
    \begin{aligned}
      \gdenot{\blank}_{1} &\defeq \evalh_{1} \comp \evalp_{1} \comp \evalt_{1}
    \end{aligned}
  \end{gather*}
\end{definition}

\begin{theorem}[Full Abstraction and Adequacy]
  If $c_1, c_2 : X \iso Y$, then $\denot{c_1} = \denot{c_2}$ iff $\gdenot{c_1}_{1} = \gdenot{c_2}_{1}$.
\end{theorem}

### 2021-07-09 Pi+/paper/finite.tex
Update

  \begin{definition}
    \label{def:group}
    In type theory, a group $G$ can be defined as a set $S$ with the following pieces of data:

@@

\begin{toappendix}
  \begin{definition}
    \label{def:free-group}
    Given a set $A$, the free group $F(A)$ on it is given by a higher inductive type with the following point and path
    constructors. Notice the similarity with the definition of a group structure (\cref{def:group}), but note that each
    operation here is a generator for $F(A)$.
    \begin{itemize}
      \item An inclusion function $\eta_{A} : A \to F(A)$
      \item A multiplication function $m : F(A) \times F(A) \to F(A)$
      \item An element $e : F(A)$
      \item An inverse function $i : F(A) \to F(A)$
    \end{itemize}
    \smallskip
    \begin{itemize}
      \item For every $x, y, z : F(A)$, a path $\term{assoc} : m(x, m(y, z)) \id m(m(x, y), z)$
      \item For every $x : F(A)$, paths $\term{unitr} : m(x, e) \id x$ and $\term{unitl} : m(e, x) \id x$
      \item For every $x : F(A)$, paths $\term{invr} : m(x, i(x)) \id e$ and $\term{invl} : m(i(x), x) \id e$
      \item A 0-truncation, for every $x, y : F(A)$ and $p, q : x \id y$, a 2-path $\term{trunc} : p \id q$
    \end{itemize}
  \end{definition}
\end{toappendix}

@@

\begin{definition}
  \label{def:presentation}
  Let $A$ be a set, and $\List[\blank]$ the free monoid. The free group $F(A)$ on $A$ is the set-quotient of $\List[A +
      A]$ by the congruence closure of the relation $a \cons \inv{a} \cons \nil \sim \nil$ and $\inv{a} \cons a \cons \nil
    \sim \nil$.
\end{definition}

@@

\begin{definition}
  Let $A$ be a set and $R : \List[A + A] \to \List[A + A] \to \UU$ a binary relation on $\List[A + A]$. The group
  $F(\langle A ; R \rangle)$ presented by $A$ and $R$, is given by the set-quotient of the free group $F(A)$ by the
  congruence closure of $R$.
\end{definition}

@@

\begin{enumerate}
  \item[\labelcref{fig:coxeter-a}] Swapping the same two elements two times in a row should be the same as doing nothing
  \item[\labelcref{fig:coxeter-b}] When swapping two distinct pairs of elements, it should not matter in which order the
        swapping happens, that is, we can slide the wires freely.
  \item[\labelcref{fig:coxeter-c}] \jk{If the next transposition in the sequence is equal to the the first one, the order of
        operations can be reversed}.

>>>>>>> ee83d6f6650c383d20e046a4ada0de4cb9c42dca
\end{enumerate}

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (0, 0)
      {braid={ s_1, s_1}};
      \node[font=\large] at (1, 0.7) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (1.6, 0)
      {braid={ 1, 1}};
    \end{tikzpicture}
    \caption{$\cancel$}
    \label{fig:coxeter-a}
  \end{subfigure}
  \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (0, 0)
      {braid={ s_1, 1}};
      \node[] at (0.7, 0.7) {\(\dots\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (1, 0)
      {braid={ 1, s_1 }};
      \node[font=\large] at (1.9, 0.7) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (2.4, 0)
      {braid={ 1, s_1}};
      \node[] at (3.1, 0.7) {\(\dots\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (3.4, 0)
      {braid={ s_1, 1}};
    \end{tikzpicture}
    \caption{$\swap$}
    \label{fig:coxeter-b}
  \end{subfigure}
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 3,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick] at (0, 0)
      {braid={ s_2, s_1, s_2}};
      \node[font=\large] at (1.4, 0.7) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 3,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick] at (2, 0)
      {braid={ s_1, s_2, s_1}};
    \end{tikzpicture}
    \caption{$\braid$}
    \label{fig:coxeter-c}
  \end{subfigure}
  \caption{Braiding diarams for Coxeter relations.}
  \label{fig:coxeter-braid}
\end{figure}

@@

\begin{proposition}
  \label{prop:nf}
  \leavevmode
  \begin{enumerate}
    \item $\longcox$ is (locally) confluent. For every span $\coxspan{w_{1}}{w_{2}}{w_{3}}$, there is a matching
          extended cospan $\coxcospan*{w_{2}}{w_{3}}{w}$.
    \item $\longcoxplus$ is terminating. For every $w \longcoxplus v$, it holds that $v < w$, where $<$ is the (well-founded)
          lexicographic ordering on $\List[\Fin[n]]$.
    \item $\longcoxstar$ is confluent. For every extended span $\coxspan*{w_{1}}{w_{2}}{w_{3}}$, there is a matching
          extended cospan $\coxcospan*{w_{2}}{w_{3}}{w}$.
    \item For every $w$, there exists a unique normal form $v$ such that $w \longcoxstar v$.~\label{prop:nf-uniqueness}
  \end{enumerate}
\end{proposition}

@@

\begin{proposition}
  \leavevmode
  \begin{enumerate}
    \item There is a group structure on $\Sn$, where the identity element is $\nil$, multiplication is given by list
          append, and inverse is given by list reversal.
    \item $\Sn$ is equivalent to the group presented by generators $\Fin[n]$ with the relations given by $\cox*$
          extended to $\List(\Fin[n] + \Fin[n])$ along the codiagonal map $\nabla_{A} : A + A \to A$.
  \end{enumerate}
\end{proposition}

@@

\begin{definition}
  Given a permutation $\sigma : \Aut[\Fin[n]]$, the inversion count of $k: \Fin[n]$ is given by
  \[ \invcount{i} = \#\Set{j < i | \sigma(j) > \sigma(i)}. \]
\end{definition}

@@

\begin{propositionrep}
  \leavevmode
  \begin{enumerate}
    \item For any Lehmer code $c$, $\immersion_{n}(c)$ is a normal form with resepct to $\longcoxstar$, that is,
          $\immersion_{n}(c)$ is in $\im{\normf}$.
    \item Any element of $\im{\normf}$ can be constructed from a unique Lehmer code by $\immersion$, that is, the fibers
          of $\immersion_{n} : \Lehmer[n] \to {\im{\normf}}$ are contractible.
  \end{enumerate}
  Therefore, there is an equivalence between $\Lehmer[n]$ and $\im{\normf}$.
\end{propositionrep}

@@

To do so, we need to construct some equivalences by counting the elements of $\Fin[n]$ using its decidable equality.
First, we define a type family $\FinExcept{n} : \Fin[n] \to \UU$ which picks out all elements in $\Fin[n]$ except
the one in the argument. Note that $\FinExcept{n}[i]$ for $i : \Fin[n]$ is a subtype of $\Fin[n]$ and is hence a
set.

\begin{definition}
  \( \FinExcept{n}[i] \defeq \dsum{j : \Fin[n]}{i \neq j} \).
\end{definition}

We state and prove a few auxiliary lemmas about how $\FinExcept{n}$ interacts with $\Fin$, these are obtained by
counting arguments using the fact that $\Fin[n]$ and $\FinExcept{n}$ both have decidable equality.

\begin{propositionrep}
  \label{prop:fin-finexcept}
  \leavevmode
  \begin{enumerate}
    % \item For any $k : \Fin[n]$, $\unit \sqcup \FinExcept{n}[k] \eqv \Fin[n]$. \label{prop:fin-finexcept-1}
    \item For any $k : \Fin[\suc[n]]$, $\FinExcept{\suc[n]}[k] \eqv \Fin[n]$. \label{prop:fin-finexcept-2}
    \item For any $n : \Nat$, \( \Aut[\Fin[\suc[n]]] \eqv \dsum{k : \Fin[\suc[n]]}{\FinExcept{\suc[n]}[n] \eqv
            \FinExcept{\suc[n]}[n - k]} \). \label{prop:fin-finexcept-3}
  \end{enumerate}
\end{propositionrep}

@@

\begin{proposition}
  \label{prop:lehmer-aut-equiv}
  For all $n:\Nat$, \( \Lehmer[n] \eqv \Aut[\Fin[\suc[n]]] \).
\end{proposition}

>>>>

  \begin{definition}[Group]
    \label{def:group}
    In type theory, a group $G$ can be defined as a set $S$ with the following pieces of data:

@@

\begin{toappendix}
  \begin{definition}[Free group]
    \label{def:free-group}
    Given a set $A$, the free group $F(A)$ on it is given by a higher inductive type with the following point and path
    constructors. Notice the similarity with the definition of a group structure (\cref{def:group}), but note that each
    operation here is a generator for $F(A)$.
    \begin{itemize}
      \item An inclusion function $\eta_{A} : A \to F(A)$
      \item A multiplication function $m : F(A) \times F(A) \to F(A)$
      \item An element $e : F(A)$
      \item An inverse function $i : F(A) \to F(A)$
    \end{itemize}
    \smallskip
    \begin{itemize}
      \item For every $x, y, z : F(A)$, a path $\term{assoc} : m(x, m(y, z)) \id m(m(x, y), z)$
      \item For every $x : F(A)$, paths $\term{unitr} : m(x, e) \id x$ and $\term{unitl} : m(e, x) \id x$
      \item For every $x : F(A)$, paths $\term{invr} : m(x, i(x)) \id e$ and $\term{invl} : m(i(x), x) \id e$
      \item A 0-truncation, for every $x, y : F(A)$ and $p, q : x \id y$, a 2-path $\term{trunc} : p \id q$
    \end{itemize}
  \end{definition}
\end{toappendix}

@@

\begin{definition}[Free group]
  \label{def:presentation}
  Let $A$ be a set, and $\List[\blank]$ the free monoid. The free group $F(A)$ on $A$ is the set-quotient of $\List[A +
      A]$ by the congruence closure of the relation $a \cons \inv{a} \cons \nil \sim \nil$ and $\inv{a} \cons a \cons \nil
    \sim \nil$.
\end{definition}

@@

\begin{definition}[Group presentation]
  Let $A$ be a set and $R : \List[A + A] \to \List[A + A] \to \UU$ a binary relation on $\List[A + A]$. The group
  $F(\langle A ; R \rangle)$ presented by $A$ and $R$, is given by the set-quotient of the free group $F(A)$ by the
  congruence closure of $R$.
\end{definition}

@@

\begin{enumerate}
  \item[\labelcref{fig:coxeter-a}] Swapping the same two elements two times in a row should be the same as doing nothing
  \item[\labelcref{fig:coxeter-b}] When swapping two distinct pairs of elements, it should not matter in which order the
        swapping happens, that is, we can slide the wires freely.
  \item[\labelcref{fig:coxeter-c}] There are two equivalent ways of swapping the first and the last element in a
  three-element sequence.
\end{enumerate}

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (0, 0)
      {braid={ s_1, s_1}};
      \node[font=\large] at (1, 0.7) {\(=\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (1.6, 0)
      {braid={ 1, 1}};
    \end{tikzpicture}
    \caption{$\cancel$}
    \label{fig:coxeter-a}
  \end{subfigure}
  \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (0, 0)
      {braid={ s_1, 1}};
      \node[] at (0.7, 0.7) {\(\dots\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (1, 0)
      {braid={ 1, s_1 }};
      \node[font=\large] at (1.9, 0.7) {\(=\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (2.4, 0)
      {braid={ 1, s_1}};
      \node[] at (3.1, 0.7) {\(\dots\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (3.4, 0)
      {braid={ s_1, 1}};
    \end{tikzpicture}
    \caption{$\swap$}
    \label{fig:coxeter-b}
  \end{subfigure}
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 3,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick] at (0, 0)
      {braid={ s_2, s_1, s_2}};
      \node[font=\large] at (1.4, 0.7) {\(=\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 3,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick] at (2, 0)
      {braid={ s_1, s_2, s_1}};
    \end{tikzpicture}
    \caption{$\braid$}
    \label{fig:coxeter-c}
  \end{subfigure}
  \caption{Braiding diarams for Coxeter relations.}
  \label{fig:coxeter-braid}
\end{figure}

@@

\begin{theorem}
  \label{prop:nf}
  \leavevmode
  \begin{enumerate}
    \item $\longcox$ is (locally) confluent. For every span $\coxspan{w_{1}}{w_{2}}{w_{3}}$, there is a matching
          extended cospan $\coxcospan*{w_{2}}{w_{3}}{w}$.
    \item $\longcoxplus$ is terminating. For every $w \longcoxplus v$, it holds that $v < w$, where $<$ is the (well-founded)
          lexicographic ordering on $\List[\Fin[n]]$.
    \item $\longcoxstar$ is confluent. For every extended span $\coxspan*{w_{1}}{w_{2}}{w_{3}}$, there is a matching
          extended cospan $\coxcospan*{w_{2}}{w_{3}}{w}$.
    \item For every $w$, there exists a unique normal form $v$ such that $w \longcoxstar v$.~\label{prop:nf-uniqueness}
  \end{enumerate}
\end{theorem}

@@

\begin{theorem}
  \leavevmode
  \begin{enumerate}
    \item There is a group structure on $\Sn$, where the identity element is $\nil$, multiplication is given by list
          append, and inverse is given by list reversal.
    \item $\Sn$ is equivalent to the group presented by generators $\Fin[n]$ with the relations given by $\cox*$
          extended to $\List(\Fin[n] + \Fin[n])$ along the codiagonal map $\nabla_{A} : A + A \to A$.
  \end{enumerate}
\end{theorem}

@@

\begin{definition}[Inversion count]
  Given a permutation $\sigma : \Aut[\Fin[n]]$, the inversion count of $k: \Fin[n]$ is given by
  \[ \invcount{i} = \#\Set{j < i | \sigma(j) > \sigma(i)}. \]
\end{definition}

@@

\begin{theoremrep}
  \leavevmode
  \begin{enumerate}
    \item For any Lehmer code $c$, $\immersion_{n}(c)$ is a normal form with resepct to $\longcoxstar$, that is,
          $\immersion_{n}(c)$ is in $\im{\normf}$.
    \item Any element of $\im{\normf}$ can be constructed from a unique Lehmer code by $\immersion$, that is, the fibers
          of $\immersion_{n} : \Lehmer[n] \to {\im{\normf}}$ are contractible.
  \end{enumerate}
  Therefore, there is an equivalence between $\Lehmer[n]$ and $\im{\normf}$.
\end{theoremrep}

@@

\begin{definition}[${\FinExcept{n}} : {\Fin[n]} \to \UU$]
  For $n : \Nat$, the type family $\FinExcept{n}$ picks out all elements in $\Fin[n]$ except the one in the argument.
  \[
    \FinExcept{n}[i] \defeq \dsum{j : \Fin[n]}{i \neq j} \).
  \]
\end{definition}

Note that $\FinExcept{n}[i]$ for $i : \Fin[n]$ is a subtype of $\Fin[n]$ and is hence a set. We state and prove a few
auxiliary lemmas about how $\FinExcept{n}$ interacts with $\Fin$ -- these are obtained by counting arguments using the
fact that $\Fin[n]$ and $\FinExcept{n}$ both have decidable equality.

\begin{lemmarep}
  \label{prop:fin-finexcept}
  \leavevmode
  \begin{enumerate}
    % \item For any $k : \Fin[n]$, $\unit \sqcup \FinExcept{n}[k] \eqv \Fin[n]$. \label{prop:fin-finexcept-1}
    \item For any $k : \Fin[\suc[n]]$, $\FinExcept{\suc[n]}[k] \eqv \Fin[n]$. \label{prop:fin-finexcept-2}
    \item For any $n : \Nat$, \( \Aut[\Fin[\suc[n]]] \eqv \dsum{k : \Fin[\suc[n]]}{\FinExcept{\suc[n]}[n] \eqv
            \FinExcept{\suc[n]}[n - k]} \). \label{prop:fin-finexcept-3}
  \end{enumerate}
\end{lemmarep}

@@

\begin{theorem}
  \label{prop:lehmer-aut-equiv}
  For all $n:\Nat$, \( \Lehmer[n] \eqv \Aut[\Fin[\suc[n]]] \).
\end{theorem}
